---
title: "Shark Population Simulation"
author: "Camille Kaczmar, Kenney Flavin, Elizabeth Braun"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sharkpopulation) # Load your package
library(ggplot2)         # For graphing
library(purrr)           # For using the map functions
```

## Generating Data for Simulation
```{r}
# Generating initial populations and growth rates for the simulations
initial_populations <- c(100, 200)
growth_rates <- c(0.1, 0.15)

# Other parameters
carrying_capacity <- 1000
time_steps <- 50
threat_factor <- 1

```


## Running Simulations
```{r}
for_loop_results <- list()

for (i in seq_along(initial_populations)) {
  for_loop_results[[i]] <- simulate_shark_population(
    initial_population = initial_populations[i],
    growth_rate = growth_rates[i],
    carrying_capacity = carrying_capacity,
    time_steps = time_steps,
    threat_factor = threat_factor
  )
}

```

## Using Purr
```{r}
purrr_results <- map2(
  initial_populations, 
  growth_rates, 
  ~simulate_shark_population(
    initial_population = .x,
    growth_rate = .y,
    carrying_capacity = carrying_capacity,
    time_steps = time_steps,
    threat_factor = threat_factor
  )
)

```

## Graphing Results
```{r}
# Combining the results into a single data frame for plotting
results_df <- data.frame(
  Time = rep(1:time_steps, 2),
  Population = c(for_loop_results[[1]], purrr_results[[1]]),
  Method = rep(c("For Loop", "Purrr"), each = time_steps)
)

# Plotting
ggplot(results_df, aes(x = Time, y = Population, color = Method)) +
  geom_line() +
  labs(title = "Shark Population Simulation Over Time",
       x = "Time Step",
       y = "Population Size") +
  theme_minimal()

```
This R Markdown document includes all the steps: generating data, running simulations with both a for loop and `purrr`, and finally graphing the results with `ggplot2`. The final plot will compare the population sizes over time between the two methods, although, in this case, the results should be identical since the same calculations are performed. 










